---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# brasileirao

R Package with the Brazilian National Soccer League (Brasileirão) matches from 2003 to 2020.

## Installation

You can install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("williamorim/brasileirao")
```

## Example

Data from the 2020 season:

```{r example}
library(brasileirao)

matches %>% 
  dplyr::filter(season == 2020)
```

## Sources

- Data from 2003 to 2019: [http://www.chancedegol.com.br/](http://www.chancedegol.com.br/)

- Data from 2020: [globoesporte.globo.com](https://globoesporte.globo.com/futebol/brasileirao-serie-a/)

## Warranty

The data in this package was not validated by any means and has no warranty.

If you find any bug or wrong information, please [open a issue](https://github.com/williamorim/brasileirao/issues).

## Next steps

- Update the data every Monday and Thursday at 11:59 pm using GitHub Actions.


